### 2020-05-26 Report/aws_325ghz_study.tex
A few changes and comments in the report file.

\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{fit_AWS-34_AWS-42}\hspace{5mm}% 
	\caption{Brightness temperature difference of AWS-34 from AWS-42 plotted
      against cloud impact in AWS-34. The black curve represents the line of
      best fit as a third order polynomial. Red and green color represent the
      clear and cloudy cases respectively in the simulation dataset. The blue
      vertical line represents a clear-sky screening threshold of 0.2\,K. }
	\label{fig:fit:c34-42}
\end{figure}
%

As an example, the relationship between the TB differences for C1 and C2 and
the cloud impact in C1 is shown in Fig.~\ref{fig:fit:c34-42}. For this
particular case, C1 is AWS-34 and C2 is AWS-42, and around 125\,000 simulations
are used. The two variables have a reasonably strong correlation for small TB
differences, but as the impact of cloud increases the correlations gets poorer.
The data can be fitted to linear or non-linear models. The fitted model can be
used to interpolate the adjustment required to compensate the brightness
temperature for cloudy cases. To avoid fitting the ``too cloudy'' cases which
do not show any reasonable correlation, cases with $Tb2-Tb1< -40$\,K are
excluded in the fit. Also, cases with $Tb2-Tb1 < 0.2$\,K (red color dots) are
assumed to be clear-sky are not included in the model.

It is also important to have a manner for making a clear/cloudy classification.
This is useful for making a filtering in line with \citep{rekha2012potential},
but is also needed in the correction scheme. The latter is the case as the
polynomial fit derived gives a non-zero correction for clear-sky cases. In
Fig.~\ref{fig:fit:c34-42} the difference between clear-sky values of channel C1
and C2 (red dots) have a mean close to zero (as the weighting functions are
well matched), but this is not the case for all channel combinations and some
general rule for finding a threshold value (with respect to $x_m$) must be
formulated. The polynomial fit will be used also for this part.

@@

\subsection{Application of correction scheme}
\begin{figure}[!p]
	\centering
	\includegraphics[clip,trim=0 0 0 0,height=90mm]{PDF_corrected_AWS-34_AWS-42}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The spread of noise is also shown as
      reference. The measurements have been corrected using brightness
      temperatures from AWS-42. The average bias values are given in parenthesis in the legend. No clear/cloudy classification based on the fit is applied, but cases with $Tb2 - Tb1 > 15$\,K are rejected.}
	\label{fig:correction:c34-42}
\end{figure}
%

\begin{figure}[!]
	\centering
	\includegraphics[height=90mm]{PDF_corrected_AWS-34_AWS-42_thinned}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction. The measurements have been
      corrected using a cubic model. The different datasets are: thinned: 50\%
      of the clear-sky cases removed, filtered (1$\sigma$): cloudy measurements
      are filtered with noise-index = 1$\sigma$, corrected (1$\sigma$): cloudy
      measurements are corrected with noise-index = 1$\sigma$, Sreerekha et al:
      cloud filtering according to criteria described in
      \cite{rekha2012potential}.}
	\label{fig:correction:c34-42:thinned}
\end{figure}
%

@@

To test the efficacy of the correction scheme, three different models: linear,
quadratic and cubic are evaluated to fit the TB differences between C1 and C2.
For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too
cloudy'' and are not corrected. The clear-sky adjustment for all eligible
measurements (without clear/cloudy classification) is calculated from all three models,
and the three predicted datasets are compared. The error in the predicted
measurements is assessed by calculating the deviation to noise-free clear-sky
observations. The occurrence frequency of the deviations from three models is
shown in Fig.~\ref{fig:correction:c34-42}. The occurence frequency of the
measurement without any filtering or correction is also plotted as reference
(orange color). If all measurements are devoid of any cloud impact, the
deviations should follow the gaussian distribution of noise. However, in real
scenarios, the distribution is skewed due to the impact of clouds. It should
also be noted that since no clear-sky screening was included in the
measurements, the measurements with zero deviation to noise-free clear-sky were
reduced. This indicates that it is extremely important to correctly classify
the cases as clear/cloudy. Among the three models, the quadratic and cubic
models work better than the linear model. Both quadratic and cubic models are
able to correct the cloud impact in the measurements, however the values of
average bias indicates that the cubic model performs better. The average
deviation in the dataset is -0.82\,K and after correction with a cubic model,
it reduces to -0.02\,K, while for quadratic model, the average bias after
correction is 0.24\,K. For all other results described in this section, a cubic
model is used.

To implement the clear/cloudy classification as discussed in the previous section, two
different values of $dtb_{cs}$ are tested: $1\sigma$ and $2\sigma$. For both values of $dtb_{cs}$ the
corresponding clear-sky cut-off ($x_{cs}$) is calculated using
Eq~\ref{eq:dtb}. Figure~\ref{fig:correction:c34-42} shows the deviation of the uncorrected and corrected measurements to their noise-free clear-sky values. The results from
\cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
for our assumptions). In order to have a fair comparison
of our approach with \cite{rekha2012potential}, we also include the dataset,``Filtered'', where all cloudy cases are rejected.  Apart from the fit based cloudy classfication, it is also assumed that cases with $Tb2-Tb1 < $ -15\,K are ``too-cloudy'', and are rejected.
Various metrics corresponding to the Figure~\ref{fig:correction:c34-42} are shown in
Table~\ref{tab:correction:stats:34:42}.

@@

In Sec.~\ref{sec:validation} the validation of simulations against ATMS data (Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were underrepresented in comparison to the observations. In order to have a better representation of the cloudy cases, we thin the measurement dataset by rejecting 50\% of the clear-sky cases. Results from this smaller dataset are shown in Table~\ref{fig:correction:c34-42:thinned}. In comparison to the original dataset, the statistics in the thinned dataset is slightly worse, as expected. But overall the performance of the correction scheme is comparable. For all further analysis presented in this report, we use the thinned dataset.
%
\subsection{Application of correction scheme using AWS-4X}
%
\begin{figure}[!t]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
	\caption{Same as Fig.~\ref{fig:correction:c34-42:thinned}, but for channel combinations: AWS-32 and AWS-4X.}
	\label{fig:correction:c32-4X:thinned}
\end{figure}
%

@@

Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations of the measurements to
clear-sky values before and after correction, and the corresponding metrics are
provided in Table~\ref{tab:correction:stats:32:4X}. Rejecting all the cloudy cases reduces the average bias in the measurements from -0.62\,K to -0.22\,K, but when these cases are corrected, the total bias increases to 0.87\,K. This indicates that the relationship between AWS-32 and AWS-4X is inadequate to estimate the cloud impact in AWS-32.
% 
\begin{table}[!h]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction \\
						&   [K]  &   [K] & skewness[K] 		& rejected [\%]\\
		\hline
Noise             		&  -0.00 &  0.45 &               0.01 &                - \\
uncorrected       		&  -0.62 &  1.77 &              -4.61 &                - \\
filtered($1\sigma$)  	&  -0.22 &  0.51 &              -0.65 &               85.37 \\
corrected($1\sigma$) 	&   0.87 &  1.75 &              -1.31 &                5.35 \\
corrected($2\sigma$) 	&   0.76 &  1.80 &              -1.08 &                5.35 \\
sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               62.95 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-4X.   }
	\label{tab:correction:stats:32:4X}
\end{table}

@@

Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is
corrected using AWS-41. The TB differences for this combination and the cloud
impact in AWS-33 are highly correlated. Rejecting the cloudy cases reduces the average bias in the measurements from -0.33\,K to -0.13\,K, while a correction of cloudy cases according to the correction scheme reduces the bias further to 0.01\,K.

A similar performance is seen for the combination AWS-35 and AWS-43, where 21\%
of the measurements are classfied as cloudy. Table~\ref{tab:correction:stats:35:43} shows the statistics obtained from this combination. The statistics from the channel combination AWS-36 and AWS-42 are shown in Table~\ref{tab:correction:stats:36:43}.
%
\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction \\
							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
		\hline
noise             		&   0.00 &  0.45 &               0.00 &                - \\
uncorrected       		&  -0.48 &  1.82 &             -14.89 &                - \\
filtered($1\sigma$)  	&  -0.26 &  0.77 &             -16.30 &               72.27 \\
corrected($1\sigma$) 	&   0.44 &  1.70 &             -14.68 &                7.93 \\
corrected($2\sigma$) 	&   0.25 &  1.72 &             -13.85 &                7.93 \\
sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               62.04 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-41.   }
	\label{tab:correction:stats:32:41}
\end{table}

>>>>

\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{fit_AWS-34_AWS-42}\hspace{5mm}% 
	\caption{Brightness temperature difference of AWS-34 from AWS-42 plotted
      against cloud impact in AWS-34. The black curve represents the line of
      best fit (of green points) as a third order polynomial. Red and green
      color represent the clear and cloudy cases respectively in the simulation
      dataset. The blue vertical line represents a clear-sky screening
      threshold of 0.2\,K. }
	\label{fig:fit:c34-42}
\end{figure}
%

As an example, the relationship between the TB differences for C1 and C2 and
the cloud impact in C1 is shown in Fig.~\ref{fig:fit:c34-42}. For this
particular case, C1 is AWS-34 and C2 is AWS-42, and around 125\,000 simulations
are used. The two variables have a reasonably strong correlation for small TB
differences, but as the impact of cloud increases the correlations gets poorer.
The data can be fitted by linear or non-linear models. The fitted model can be
used to obtain the adjustment required to compensate the brightness
temperature for cloudy cases. To avoid fitting the ``too cloudy'' cases which
do not show any reasonable correlation, cases with $Tb2-Tb1< -40$\,K are
excluded in the fit. Also, cases with $Tb2-Tb1 < 0.2$\,K (red color dots) are
assumed to be clear-sky are not included in the model.

It is also important to have a manner for making a clear/cloudy classification.
This is useful for making a filtering in line with \citet{rekha2012potential},
but is also needed in the correction scheme. The latter is the case as the
polynomial fit derived gives a non-zero correction for clear-sky cases. In
Fig.~\ref{fig:fit:c34-42} the difference between clear-sky values of channel C1
and C2 (red dots) have a mean close to zero (as the weighting functions are
well matched), but this is not the case for all channel combinations and some
general rule for finding a threshold value (with respect to $x_m$) must be
formulated. The polynomial fit will be used also for this part.

@@

\subsection{Application of correction scheme}
\begin{figure}[!p]
	\centering
	\includegraphics[clip,trim=0 0 0 0,height=80mm]{PDF_corrected_AWS-34_AWS-42}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The spread of noise is also shown as
      reference. The measurements have been corrected using brightness
      temperatures from AWS-42. The average bias values are given in parenthesis in the legend. No clear/cloudy classification based on the fit is applied, but cases with $Tb2 - Tb1 > 15$\,K are rejected.}
	\label{fig:correction:c34-42}
\end{figure}
%

\begin{figure}[!p]
	\centering
	\includegraphics[height=80mm]{PDF_corrected_AWS-34_AWS-42_thinned}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction. The measurements have been
      corrected using a cubic model. The different datasets are: thinned: 50\%
      of the clear-sky cases removed, filtered (1$\sigma$): cloudy measurements
      are filtered with noise-index = 1$\sigma$, corrected (1$\sigma$): cloudy
      measurements are corrected with noise-index = 1$\sigma$, Sreerekha et al:
      cloud filtering according to criteria described in
      \cite{rekha2012potential}.}
	\label{fig:correction:c34-42:thinned}
\end{figure}
%

@@

To test the efficacy of the correction scheme, three different models: linear,
quadratic and cubic are evaluated to fit the TB differences between C1 and C2.
For all three models, cases with $Tb2-Tb1 < $ -15\,K are assumed to be ``too
cloudy'' and are not corrected. The clear-sky adjustment for all eligible
measurements (without clear/cloudy classification) is calculated from all three
models, and the three predicted datasets are compared. The error in the
predicted measurements is assessed as the deviation to corresponding noise-free
clear-sky value.

The occurrence frequency of the deviations from three models is shown in
Fig.~\ref{fig:correction:c34-42}. The occurence frequency of the measurement
without any filtering or correction is also plotted as reference (orange
color). If all measurements are devoid of any cloud impact, the deviations
should follow the gaussian distribution of noise. However, in real scenarios,
the distribution is skewed due to the impact of clouds. It should also be noted
that since no clear-sky screening was included in the measurements, the
measurements with zero deviation to noise-free clear-sky were reduced. [* Don't
get what you mean here * ] This
indicates that it is extremely important to correctly classify the cases as
clear/cloudy. Among the three models, the quadratic and cubic models work
better than the linear model. Both quadratic and cubic models are able to
correct the cloud impact in the measurements, however the values of average
bias indicates that the cubic model performs better. The average deviation in
the dataset is -0.82\,K and after correction with a cubic model, it reduces to
-0.02\,K, while for quadratic model, the average bias after correction is
0.24\,K. For all other results described in this section, a cubic model is
used.

[* The text seems to indicate that you here move to Fig 11, but you refer to
Fig 10. *]

To implement the clear/cloudy classification as discussed in the previous
section, two different values of $dtb_{cs}$ are tested: $1\sigma$ and
$2\sigma$. For both values of $dtb_{cs}$ the corresponding clear-sky cut-off
($x_{cs}$) is calculated using Eq~\ref{eq:dtb}.
Figure~\ref{fig:correction:c34-42} shows the deviation of the uncorrected and
corrected measurements to their noise-free clear-sky values. The results from
\cite{rekha2012potential} are also shown as reference (see Sec.~\ref{sec:rekha}
for our assumptions). In order to allow a more direct comparison of our
approach with \cite{rekha2012potential}, we also include the
dataset,``Filtered'', where all cloudy cases are rejected. Apart from the fit
based cloudy classfication, it is also assumed that cases with $Tb2-Tb1 < $
-15\,K are ``too-cloudy'', and are rejected. Various metrics corresponding to
the Figure~\ref{fig:correction:c34-42} are shown in
Table~\ref{tab:correction:stats:34:42}.

@@

In Sec.~\ref{sec:validation} the validation of simulations against ATMS data
(Fig.\ref{fig:pdf:c16-22}) showed that the cloudy cases in the simulations were
underrepresented in comparison to the observations. In order to have a better
representation of the cloudy cases, we thin the measurement dataset by
rejecting 50\% of the clear-sky cases. Results from this smaller dataset are
shown in Table~\ref{fig:correction:c34-42:thinned}. [* You mean FIgure? But you
should the also refer to Table 5. *]In comparison to the
original dataset, the statistics in the thinned dataset is slightly worse, as
expected. But overall the performance of the correction scheme is comparable.
For all further analysis presented in this report, we use the thinned dataset.
%
\subsection{Application of correction scheme using AWS-4X}
%
\begin{figure}[!t]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
	\caption{Same as Fig.~\ref{fig:correction:c34-42:thinned}, but for channel combinations: AWS-32 and AWS-4X.}
	\label{fig:correction:c32-4X:thinned}
\end{figure}
%

@@

Fig.~\ref{fig:correction:c32-4X:thinned} shows the deviations of the
measurements to clear-sky values before and after correction, and the
corresponding metrics are provided in Table~\ref{tab:correction:stats:32:4X}.
Rejecting all the cloudy cases reduces the average bias in the measurements
from -0.62\,K to -0.22\,K, but when these cases are corrected, the total bias
increases to 0.87\,K. This indicates that the relationship between AWS-32 and
AWS-4X is inadequate to estimate the cloud impact in AWS-32.
[* You should discuss the high fraction reject we get for ``filtered'', but is
this the best we can do? *]

%
\begin{table}[!h]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction \\
						&   [K]  &   [K] & skewness[K] 		& rejected [\%]\\
		\hline
Noise             		&  -0.00 &  0.45 &               0.01 &                - \\
uncorrected       		&  -0.62 &  1.77 &              -4.61 &                - \\
filtered($1\sigma$)  	&  -0.22 &  0.51 &              -0.65 &               85.37 \\
corrected($1\sigma$) 	&   0.87 &  1.75 &              -1.31 &                5.35 \\
corrected($2\sigma$) 	&   0.76 &  1.80 &              -1.08 &                5.35 \\
sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               62.95 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-4X.   }
	\label{tab:correction:stats:32:4X}
\end{table}

@@

Table~\ref{tab:correction:stats:33:41} shows the statistics when AWS-33 is
corrected using AWS-41. The TB differences for this combination and the cloud
impact in AWS-33 are highly correlated. Rejecting the cloudy cases reduces the
average bias in the measurements from -0.33\,K to -0.13\,K, while a correction
of cloudy cases according to the correction scheme reduces the bias further to
0.01\,K. [* Last value not consistent with table *]

A similar performance is seen for the combination AWS-35 and AWS-43, where 21\%
of the measurements are classfied as cloudy.
Table~\ref{tab:correction:stats:35:43} shows the statistics obtained from this
combination. The statistics from the channel combination AWS-36 and AWS-42 are
shown in Table~\ref{tab:correction:stats:36:43}. [* Add a bit of discussion for
both combiniations. *]

[* Should not the fraction of rejected for Sreerekha et al be the same for all
channel combinations? *]

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   measure & fraction \\
							&   [K]  &   [K] & skewness[K] & rejected [\%]\\
		\hline
noise             		&   0.00 &  0.45 &               0.00 &                - \\
uncorrected       		&  -0.48 &  1.82 &             -14.89 &                - \\
filtered($1\sigma$)  	&  -0.26 &  0.77 &             -16.30 &               72.27 \\
corrected($1\sigma$) 	&   0.44 &  1.70 &             -14.68 &                7.93 \\
corrected($2\sigma$) 	&   0.25 &  1.72 &             -13.85 &                7.93 \\
sreerekha et al   		&  -0.41 &  1.00 &              -2.54 &               62.04 \\
		\hline
	\end{tabular}
	\caption{Same as Table~\ref{tab:correction:stats:34:42}, but for channel combinations: AWS-32 and AWS-41.   }
	\label{tab:correction:stats:32:41}
\end{table}
